\poemtitle{EP 1: Chicken Wing Factory - How June and Ru D. Met}

It was just another boring delivery mission from planet Dermania. 

A red box, with a bunch of ``Fragile'' stickers above it. Its destination: the famous EH chicken wing factory by Doctor Wing. 

Ru D. thought he heard some weird noises inside the box, but remembered that butting in The Government's business always brought trouble, especially these days. 

It had only been two weeks since he became subjected to disciplinary punishment from The Government. And that was exactly the reason he was doing these boring D-rank missions after being impounded with all the weapons he loved. 

With the box in his hand, he entered the Factory lobby. It was full of ad posters, slogans with ``Our Chicken wings make the Earth Happy!'', ``Best Tech for Best Chicken Wings'' etc. The lobby guy told him to wait, spraying air freshener around him.

After a couple of minutes waiting, an old guy with a strong fry oil scent stood before Ru D.: it was Doctor Wing. The lobby guy's powerful spraying started again. Ru D. checked his ID card, and handed the red box. 

``Please sign here,'' Ru D. said.

Doctor Wing raised his hand to sign. Suddenly, the whole building was blacked out. Screams filled the lobby, with giant shadows making creepy noises via blurry lights. 

``ALIEN INVASION!'' somebody shouted. An ear-piercing siren started ringing in the lobby. Ru D. got a grip on himself. He realized that both the box and Doctor Wing had already disappeared. The issue was that the signature was not done. 

``Oh, crap,'' Ru D. thought.
The signature needs to be done. Or at least the box should be retrieved. Ru D. didn't want any more punishments. He started crawling slowly following the strong fry oil scent from Doctor Wing. 

``Ugh...'' It was Doctor Wing's voice. Ru D. rushed. Doctor Wing was knocked out at the corner of a silent room.

``Sir? Sir? Wake up!'' Ru D. was desperately slapping Wing's face to wake him up. \\
``Please feel free to die but NOT before you sign here! Please!'' \\
``Ugh... bring my—'' \\
``Yes yes, your pen is here!'' \\
``No... not this... but...'' 

While Ru D. was struggling to make the doctor hold his pen, suddenly the lights turned on. Dermanians, 50cm-tall and fully armed, were surrounding them. The smallest guy came forward.

``Identify yourself,'' he asked. \\
``Um...'' 

While Ru D. was confused without knowing what to say, Wing shouted:
``He is the Doctor Wing!''\\
``Eh? Me? What the—''\\
``Grab him!''

Small Dermanians were about to dive towards Ru D. when a short flashback began flowing in his head, starting with

``I really shouldn't punch my boss,'' and ending with \\
``But I really hate this job...'' 

Suddenly the floor around Ru D. collapsed. Angry faces of Dermanians were getting smaller and smaller. There was nothing he could do but just fall down to the dark and deep deep hole. 

Ru D. opened his eyes. Closed-up and curious eyes were piercing him.

``ARGH!!!!'' he shouted. \\
``Oh! You woke up!'' said the curious woman.

Ru D. was sprawling on a desk. He slowly stood up grabbing his dizzy head. This smell of dampness... The underground? 

``Welcome to my office! I'm researcher June! I just made a new song by the way. I thought it would be great to listen to it all together in this building. So I installed these speakers towards the ceiling and played, then you suddenly fell down here! You literally fell into my music! I'm so glad to meet my fan!'' 

Maybe she is a bit crazy. Without a word, Ru D. tried to open the doors, but they were all locked.

``Oh, you can't get out this way. 5 years ago I invented the `Crispy Again Gun' that transforms soggy chicken wings into crispier ones. But Doctor Wing said I was useless so he locked me here. But now I have improved the performance! I'm sure he will love this now! Do you wanna come with me to show this to the doctor?'' 

Still, he was not listening. But he also wanted to meet Doctor Wing for several other reasons. He furrowed his brow looking at the locked door and the giant hole in the ceiling.

``Um... Did you say a song? Can we listen to it again?'' \\
``OMG you are the first one who asks me to play my music! I'll show you my favo—'' \\
``No no, just the very last one that you played. I love it. Let everybody listen to this again!''

He installed the speakers towards the locked door and pushed the play button.  \\
Crash! The door was blown away.

``This is the best song I've ever heard,'' said Ru D. \\
``You've listened for only 1 sec!'' \\
``We have no time for this. Alien invaded this factory. They saw me falling down here, so we have to get out of here before they come.''

The underground was built like a maze. Not knowing if they were heading the right way, they just walked, walked and walked. 

\emph{Bump!}

Ru D. fell hard after stepping on something. An emptied red box, which looked quite similar to what he delivered today. 

``Are you alright dear?''

Ru D. looked behind following June's kind voice. But she was not talking to him. But to a... smaller Dermanian?

``Or are you invading the Earth too?'' she added.

The child shook his head, saying he just wanted to go home. He was about to burst out crying. 

Ru D. urgently dashed to the kid.

``No no no no, don't cry! The aliens... I mean, some people might hear us! Shush shush... shhh...''

Ru D. was in a flurry and tried to soothe the child. Carrying the sleeping child on the back, Ru D. and June kept moving. 

Then they encountered another Dermanian child. After an hour, Ru D. was carrying at least 20 sleeping Dermanian children. June had already disappeared half an hour ago.

Finally, he found the exit. It was bright outside. The first thing that Ru D. encountered in the exit was Doctor Wing. He was running away. Armed Dermanians were hunting him from behind. Doctor Wing saw Ru D. and the children and started laughing loudly. 

``HAHAHAHA! You delivery guys are so fast and accurate! Again, you delivered all the children on a platter at the perfect timing!''

He took out a gun and aimed at the children hanging on Ru D.:

``Everything shot by this Wing Gun turns into a delicious chicken wing! Drop your weapons! Then at least these children will be safe on your planet. Or should I say... These children will become the best crispy chicken wings one by one!'' 

Doctor Wing fired a warning shot towards a rock on the floor. The rock instantly changed to a chicken wing. Soon a delicious smell spread out all over the hall. Dermanians started to drop their weapons. 

``That's right, that's right. I've been studying chicken wings for 30 years. And this Wing Gun is the masterpiece of my research life! And you know what? My calculation shows that the chicken wings made out of Dermanians are the best for a human's tongue! Now gently be crispy and contribute to human's happiness on this Earth!''

``NOOOOO!!!''

Doctor Wing started firing randomly. Everyone in the hall became a chicken wing. Even Ru D. who was blocking the children became a crispy chicken wing. Fry oil scent filled the place. Doctor Wing was standing in the middle of the hall alone, with a satisfied face.

A couple of minutes later, a familiar voice was heard from the underground stairs. \\
``Exit! Here is the exit!'' It was June with Dermanian children. \\
``OH! Doctor Wing! There you were! Wow! What happened? Chicken wings and rocks are everywhere! Is it a new decoration for the lobby?'' \\
``Get to the point!'' he replied. \\
``I improved the performance of the Crispy Again Gun! I'm sure you will love this!''  

Doctor Wing left the hall leaving June behind. \\
``Oh comm'n! Take a look! 5 years ago it could only rewind chicken wings crispiness by 1 second, but now it can rewind by 10 minutes! So it can be crispy all the time even if time passes! Doc! Don't go! Look!''

June shot one of the chicken wings using her Crispy Again Gun. The chicken wing transformed into Ru D., then June looked at him and the gun one by one with a confused face.

Awkward blinks were exchanged between them. June mumbled tilting her head.

``Is it a new bug? This should rewind 10 mins to make it crispier...? Or.... Oh!! Are you the spirit of chicken wings? Then take a look!'' \\
She shot another chicken wing. It turned into a Dermanian. \\
Another confused blinks were exchanged between them. Doctor Wing looked behind with an ominous feeling. 

Ru D. quickly shouted at June.
``I'LL EXPLAIN LATER JUST KEEP SHOOTING THE CHICKEN WINGS!''  \\
Ru D. dived towards Doctor Wing. Doctor Wing swiftly took out his Wing Gun from his pocket and pointed at Ru D., who started kicking the rocks on the floor. Numerous rocks were floating between the two men.
Pew Pew Pew!!!

Numerous chicken wings fell on the floor. Except one. It was being chewed between Ru D.'s teeth. \\
``Weh, not as good as I expected'' \\
Doctor Wing glared at Ru D. fiercely. Then with a click sound, the Wing Gun started to absorb the doctor's hand. His muscles started to swell too. \\
``I'll show you... the real spirit of the Chicken Wing!!!''

The chasing started. Avoiding the bullets, Ru D. observed the doctor. He was trained. Recharging speed? After the transformation, it became almost instant. Shields? Useless, they would just be turned into chicken wings. Asking June to shoot the time-rewind-gun to the doctor? No, bringing Dermanians back to life was more urgent.
While he kept thinking, something was rattling under his feet. Air freshener?

Just at the time the doctor shot the gun, Ru D. sprayed the freshener towards the bullet. Thousands of aerosols from the spray touched the bullet at the same time, and turned into chicken wings. They busted and rained between them like popcorn. In that short moment, the view was shielded. Ru D. easily snatched the doctor's arm and hit it.

``AAAAARRRGGGGHHH MY GUUUN!!!!!!!'' \\
Doctor Wing painfully howled looking at his dangling arm and the chicken gun.
Ru D. smiled and took out his rugged sign pad. \\
``Well, it seems like you can't use the gun and the arm anymore! But at least you can sign here!'' \\
Doctor Wing started chuckling with a low voice. Then suddenly he dashed to where June and Dermanians were hiding.

Meanwhile, June, who was almost dancing to avoid the random gun shooting and picking up the chicken wings, safely revived all the Dermanians behind the wall. While they were carefully searching for an escape route, Doctor Wing showed up. A startled June spontaneously aimed the Crispy Again Gun at Doctor Wing. Pew.

``Hey! NOOOOO!!!!!!'' \\
Doctor Wing's body was restored to 10 mins ago. Which means, he was fully healed. \\
``HAHAHAHA finally June is useful in this world! Great, wait here, I'll finish off that brat first and then will enjoy crispy chicken wings made by Dermanians!!!''

Doctor Wing locked out everybody and dashed out towards Ru D. at once. Behind a small crack, June could see the second round of the fight. Calming her breath, this time she aimed at Ru D., but Doctor Wing noticed it first. Wing jumped and stretched his arm, blocking the bullet flying to Ru D. while healing Wing's small scars inflicted by Ru D., all gone.

``HAHAHA YES, I FEEL SO ENERGIZED RIGHT NOW!'' \\
Ru D. stared at June with blaming eyes. Another flashback was streaming in his head. At that moment, Doctor Wing started screaming. Small electric lights were covering his body. June shouted over the wall. \\
``Ooh! Sorry! I forgot to mention a side effect Doctor! If it is shot twice, it rewinds by 50 years!'' \\
With the mixture of scratchy sounds and screaming, Doctor Wing's body started to shrink.
 
After a brief moment of silence, there was a baby inside oversized clothes. Without knowing what just happened, the baby was smiling. \\ \\
Ru D. walked towards the baby. He took out his rugged sign pad and got the baby's scribbles on it. \\
Opening the locked door, Ru D. stared at the Crispy Again Gun in June's hand. And he asked:

``You need a job?''